%-------------------------
% Resume in LaTeX (Tarun Kumar Allamsetty)
% Based on template by Sourabh Bajaj – MIT License
%-------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{latexsym}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Tarun Kumar Allamsetty} & Email: \href{mailto:tarunkumar.allamsetty@gmail.com}{tarunkumar.allamsetty@gmail.com} \\
  \href{https://github.com/Tarun-Kumar07}{github.com/Tarun-Kumar07} & Phone: +1 (919) 904-6718 \\
  \href{https://www.linkedin.com/in/tarun-kumar-allamsetty}{linkedin.com/in/tarun-kumar-allamsetty} &
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading{Duke University}{Durham, NC}
  {M.S. in Electrical and Computer Engineering (Quantum Computing Track)}{Aug 2025 -- Present}
  \resumeItemListStart
    \resumeItem{Scholarship}{Duke ECE Merit Award – \$3,386 per semester for three full-time semesters.}
  \resumeItemListEnd
  \resumeSubheading{College of Engineering Pune (Technological University)}{Pune, India}
  {B.Tech in Electronics and Telecommunication Engineering}{Aug 2018 -- May 2022}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading{ION Group}{Pune, India}
  {Software Engineer – Foundation \& iCM Platform}{Jun 2022 -- Jun 2025}
  \resumeItemListStart
    \resumeItem{Performance Optimization}{Reduced data-load time from 21 min to 7.5 sec using flame-graph profiling.}
    \resumeItem{Data Engine Design}{Developed in-memory calculation engine for availability and limit computations (FNMA).}
    \resumeItem{Rule-Based Frameworks}{Built filters and timezone handlers for scalable data classification and validation.}
    \resumeItem{Testing Infrastructure}{Implemented Cucumber test suite covering 92\% of code with 1000+ scenarios.}
    \resumeItem{System Quality}{Delivered zero post-production bugs and implemented diagnostic logging for traceability.}
    \resumeItem{Leadership}{Led onboarding sessions on SOLID principles and clean code for three years in a row.}
  \resumeItemListEnd
  \resumeSubheading{Securonix}{Pune, India}
  {Security Software Engineer Intern}{May 2021 -- Aug 2021}
  \resumeItemListStart
    \resumeItem{Threat Detection Automation}{Developed Flask tool to transfer and process IOCs, improving detection speed.}
    \resumeItem{Backend Scripts}{Automated SQL and web-scraping tasks to optimize team operations and reporting.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Quantum Computing Projects \& Open Source Contributions}
\resumeSubHeadingListStart
  \resumeSubItem{PennyLane}{
    Enhanced testing framework by implementing \texttt{assert\_equal} for detailed operator comparisons (PR \#5780);
    implemented \texttt{QutritChannel} for qutrit noise models (PR \#5793); improved shot-sampling efficiency with 
    \texttt{shots.bins()} (PR \#5476).}
  \resumeSubItem{Amazon Braket Python SDK}{
    Resolved Issue \#603 by handling conflicts between FreeParameter names and OpenQASM reserved keywords (PR \#999).}
  \resumeSubItem{Qiskit}{
    Contributed fix for Issue \#12106 to address \texttt{synth\_cnot\_count\_full\_pmh} in linear reversible circuit synthesis.}
  \resumeSubItem{Qbraid-QIR}{
    Reported missing Base Profile support in generated QIR (Issue \#215); community subsequently implemented fix.}
  \resumeSubItem{Quantum Tic Tac Toe}{
    Designed an educational game demonstrating superposition, entanglement and measurement; packaged with Docker and 
    Streamlit for deployment. Source: \href{https://github.com/Tarun-Kumar07/QuantumTicTacToe}{GitHub}.}
\resumeSubHeadingListEnd

%-----------WORKSHOPS-----------------
\section{Workshops \& Certifications}
\resumeSubHeadingListStart
  \resumeSubItem{IBM Quantum Challenge 2024}{Completed challenge problems on IBM Quantum hardware platforms.}
  \resumeSubItem{Qiskit Global Summer School 2024}{Focused on quantum systems and algorithms.}
  \resumeSubItem{QHack 2024}{Placed Top 100 in coding challenges.}
  \resumeSubItem{UnitaryHack 2024}{Solved four open-source quantum bounties.}
  \resumeSubItem{IBM Quantum Explorer Advanced Badge}{Achieved Advanced Badge status on IBM Quantum Explorer.}
\resumeSubHeadingListEnd

%-----------SCHOLARSHIPS-----------------
\section{Scholarships}
\resumeSubHeadingListStart
  \resumeSubItem{Duke ECE Merit Award}{Awarded \$3,386 per semester for three semesters at Duke University.}
\resumeSubHeadingListEnd

%-----------TEACHING AND MENTORSHIP-----------------
\section{Teaching \& Mentorship Experience}
\resumeSubHeadingListStart
  \resumeSubItem{ION Group}{
    Conducted onboarding for new undergraduate hires for three years; mentored team members in iCM Limits architecture.}
  \resumeSubItem{DSAI Club, COEP}{
    Delivered technical sessions on machine learning research (Efficient Net paper and hyperparameter tuning).}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------------
\section{Technical Skills}
\begin{itemize}[leftmargin=*]
  \item \textbf{Languages:} Python, Java, SQL, C++
  \item \textbf{Quantum Tools:} Qiskit, PennyLane, Amazon Braket, Qbraid
  \item \textbf{Frameworks:} Flask, Streamlit, Docker, Angular
  \item \textbf{Concepts:} Quantum Noise Models, Circuit Synthesis, Performance Optimization, Test Automation
\end{itemize}

%-----------RESEARCH INTEREST-----------------
\section{Research Interest}
Interested in experimental quantum computer realizations, with emphasis on qubit control, stabilization and device 
calibration to advance scalable and reliable quantum hardware development [1].

\end{document}
