%-------------------------
% Resume in LaTeX
% Author : Sourabh Bajaj
% License : MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure ATS parsing
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

\newcommand{\resumeHeading}[4]{
  \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small#4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textit{\small#1} & \textit{\small#2} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING -----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/Tarun-Kumar07}{\Large Tarun Kumar Allamsetty}} &
  Email: \href{mailto:tarunkumar.allamsetty@duke.edu}{tarunkumar.allamsetty@duke.edu} \\
  \href{https://github.com/Tarun-Kumar07}{Github}, \href{https://www.linkedin.com/in/tarun-kumar-allamsetty/}{LinkedIn} &
  Mobile: \href{tel:+19199046718}{+1-919-904-6718} \\
\end{tabular*}

%----------- EDUCATION -----------------
\section{Education}
\resumeSubHeadingListStart

  \resumeSubheading
    {Duke University}{Durham, NC}
    {M.S. in Electrical and Computer Engineering (Quantum Computing)}
    {Aug 2025 - May 2027}

  \resumeSubheading
    {COEP Technological University}{Pune, India}
    {B.E. in Electronics and Telecommunication; GPA: 8.63/10.0}
    {Aug 2018 - May 2022}

\resumeSubHeadingListEnd

%----------- OPEN SOURCE CONTRIBUTIONS -----------------
\section{Open Source Contributions}
\resumeSubHeadingListStart

  \resumeSubheading
    {\textbf{Pennylane}}{}
    {Python framework for quantum programming}{}
    \resumeItemListStart
      \resumeItem
        {Enhanced the unit testing suite for a library with 200+ contributors by
        refactoring the operator‑equality method to return detailed mismatch information, improving
        the developer experience with actionable debugging context.}
      \resumeItem
        {Optimized internal sampling logic in shots.bins(), achieving a
        50\% increase in shot‑sampling efficiency.}
    \resumeItemListEnd

  \resumeSubheading
    {\textbf{Amazon Bracket SDK}}{}
    {Python SDK for quantum hardware}{}
    \resumeItemListStart
      \resumeItem
        {Resolved a naming conflict by validating against OpenQASM‑reserved identifiers,
        eliminating runtime errors and ensuring reliable execution of parameterized circuits.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- EXPERIENCE -----------------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Ion Group}{Pune, Maharashtra}
    {Software Engineer 1}{June 2022 -- June 2025}
    \resumeItemListStart
      \resumeItem
        {Optimized application data load logic using flame graph analysis, reducing load time from 
        21 minutes to 7.5 seconds.}
      \resumeItem
        {Improved iteration performance by 52\% (6.98 ms to 3.3 ms) through targeted optimization of 
        Java HashMap operations in critical calculation paths.}
      \resumeItem
        {Accomplished cross-team standardization of approval logic (adopted by 5 teams) by 
        architecting a reusable workflow module using enterprise Java backend patterns and a 
        proprietary internal framework.}
      \resumeItem
        {Refactored a shared Angular 13 frontend used by 5+ teams by extracting 2,000+ lines of 
        duplicated logic into reusable Angular components, improving UI consistency and maintainability.}
      \resumeItem
        {Built an integration testing framework in Java using Cucumber and Mockito, with dependency 
        injection via Guice, reducing manual testing effort and improving release reliability.}
      \resumeItem
        {Developed a rule-based date resolution system in Java 8 using functional programming 
        (streams, comparators) and attribute-based matching to determine the correct current date 
        for entities.}
    \resumeItemListEnd

  \resumeSubheading
    {Securonix}{Pune, Maharashtra (Remote)}
    {Software Engineer Intern}{May 2021 -- Aug 2021}
    \resumeItemListStart
      \resumeItem
        {Engineered Python tools to parse XML security policy data across 100+ of configurations, 
        generating detailed Excel reports that accelerated identification of
        inconsistent attributes and improved policy alignment accuracy.}
      \resumeItem
        {Designed a proof‑of‑concept Flask web interface for Artemis, a central submission
        system for Indicators of Compromise (IOCs) and basic http authentication.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%----------- Projects -----------------
\section{Projects}
\resumeSubHeadingListStart
\resumeSubItem{\textbf{Quantum Tic Tac Toe} : An educational game demonstrating quantum‑mechanics concepts  through classic gameplay deployed on \href{https://quantumtictactoe-ekm2cauxbumdelekkkaxqz.streamlit.app}{Streamlit}  and containerized with Docker for local use.}
\resumeItemListEnd

%----------- SKILLS -----------------
\section{Skills}
Python, Java, Git, Docker, CI/CD (Jenkins), Linux, Cucumber, Flask, Streamlit 

%-------------------------------------------
\end{document}
